Generative Simplex Mapping: Nonlinear Endmember Extraction and Unmixing for Hyperspectral Imagery

### 2024-07-15 paper/paper.tex
added idea to discussion about parallel GTM for large datasets

- Discuss  extensions to the GSM
    - batch training as outlined in Bishop paper, extensions to noise model to allow adaptive uncertainty for each wavelength bin

>>>>

- Limitations of the GSM
    - slow training due to computation of dinstance matrix between full dataset and embedding space
    - An incremental version of the EM procedure as described in \cite{gtm-developments} can speed this up by considering batches $X_b$ of $X$ and performing only a partial E-step by updating responsibilities corresponding to the data batch
    - However, M step still involves the "full" responsibility matrix. 
    - This can be addressed by taking an ensembling approach as described in \cite{parallel-gtm} where multiple GTM are trained on subsets of $X$ and the results are averaged. 
    - More generally, we may consider a mixture-of-GTMs as briefly desribed in \cite{gtm-orig} whereby the overall density is given as 
    \begin{equation}
        p(\mathbf{x}) = \sum_r P(r)p(\mathbf{x}\vert r)
    \end{equation}
    where there are $r$ individual GTM models with mixing coefficients $P(r)$ such that $\sum_r P(r) =1$
